\documentclass[12pt]{report}

\usepackage{setspace}
%\setstretch{2.5} % for custom spacing
\setlength{\parindent}{4em}

\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{geometry}

\geometry{letterpaper, portrait, margin=1in}

%%%Title Page%%%
\title{
  Lab 03
\bigbreak BINBCD
}

\author{
{\normalsize
\begin{tabular}{l r r}
 & \textbf{Brian Weber} & \textbf{Zachary Davis}\\
\textbf{Category} & --- & zachdav@uga.edu\\
\hline
In-lab Work & 50 & 50\\
Lab Report Writing & 50 & 50\\
\end{tabular}
}
}

\date{\bigskip
\today}
%%%%%%%%%%%%


\begin{document}
\maketitle

\section*{Question 5-7}
	\paragraph{}
		Convert the 16-bit number in \$D500-\$D501 and each of the eight bit numbers in \$DB00-\$DB04
		to decimal and enter the information in the table below.  Repeat with a number between 00FF-0FFF.
		FInally, repeat this with a number between 0FFF-FFFF.
		
		\author{
		{\normalsize
		\begin{center}
		\begin{tabular}{l r r r r r r}
		& \textbf{} & \textbf{}\\
		\textbf{\$D500-\$D501 in Binary} & \textbf{\$D500-\$D501 in Hex} & \textbf{\$DB00} & \textbf{\$DB01}
		& \textbf{\$DB02} & \textbf{\$DB03} & \textbf{\$DB04}\\
		\hline
		187 & BB & 0 & 0 & 1 & 8 & 7\\
		4090 & FFA & 0 & 4 & 0 & 9 & 0\\
		56797 & DDDD & 5 & 6 & 7 & 9 & 7\\
		\end{tabular}
		\end{center}
		}
		}

\section*{Question 8}
	\paragraph{•}
		Choose a number between 10,000 and 65,535 to be stored in \$D500 and \$D501.  "Execute" the program 
		by hand and write down the impact of each instruction on the registers and memory locations involved in it.
		\vspace{1cm}
		\\Depending on the decimal or hexadecimal value you choose will effect when exactly in the program the 
		value of certain flags will be 1 or 0.  What we definitely know is that every program will effect the Zero, 
		Carry, and Overflow CPU registers.  
	
\section*{Question 9}
	\paragraph{}
		What do you think the program is doing?
		\vspace{1cm}
		\\This program is taking the value stored in \$D500 and converting it as the higher byte to decimal and
		taking the value stored in \$D501 as the lower byte to decimal.  In other words with \$D500 being the lower
		byte and \$D501 being the lower byte the value stored in them is converted from hexidecimal to decimal.
	
\section*{Question 10}
	\paragraph{}
		What do you think that XGDX is doing?
		\vspace{1cm}
		\\This instruction swaps the value in accumulator D with the value in the X register.  This is a more effective
		and efficient way to do this conversion than constantly pushing and pulling from a stack.
		
\end{document}